\documentclass[11.5pt]{article}

%\usepackage{geometry}
\usepackage[inner=0.9in,outer=0.9in,top=2.5cm,bottom=2.5cm]{geometry}
\pagestyle{empty}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{fancyhdr, lastpage, bbding, pmboxdraw}
\usepackage[usenames,dvipsnames]{color}
\definecolor{darkblue}{rgb}{0,0,.6}
\usepackage[colorlinks,pagebackref,pdfusetitle,urlcolor=darkblue,citecolor=darkblue,linkcolor=darkred,bookmarksnumbered,plainpages=false]{hyperref}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\pagestyle{fancyplain}
\fancyhf{}
\lhead{ \fancyplain{}{The Art of the Game} }
%\chead{ \fancyplain{}{} }
\rhead{ \fancyplain{}{\today} }

\thispagestyle{plain}

%%%%%%%%%%%% LISTING %%%
\usepackage{listings}
\usepackage{caption}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\textwidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}
\usepackage{verbatim} % used to display code
\usepackage{fancyvrb}
\usepackage{acronym}
\usepackage{amsthm}
\VerbatimFootnotes % Required, otherwise verbatim does not work in footnotes!
\usepackage[utf8]{inputenc}
\usepackage{enumitem}




\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{CadetBlue}{cmyk}{0.62,0.57,0.23,0}
\definecolor{lightlightgray}{gray}{0.93}



\lstset{
%language=bash,                          % Code langugage
basicstyle=\ttfamily,                   % Code font, Examples: \footnotesize, \ttfamily
keywordstyle=\color{OliveGreen},        % Keywords font ('*' = uppercase)
commentstyle=\color{gray},              % Comments font
numbers=left,                           % Line nums position
numberstyle=\tiny,                      % Line-numbers fonts
stepnumber=1,                           % Step between two line-numbers
numbersep=5pt,                          % How far are line-numbers from code
backgroundcolor=\color{lightlightgray}, % Choose background color
frame=none,                             % A frame around the code
tabsize=2,                              % Default tab size
captionpos=t,                           % Caption-position = bottom
breaklines=true,                        % Automatic line breaking?
breakatwhitespace=false,                % Automatic breaks only at whitespace?
showspaces=false,                       % Dont make spaces visible
showtabs=false,                         % Dont make tabls visible
columns=flexible,                       % Column format
morekeywords={__global__, __device__},  % CUDA specific keywords
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{center}
{\Large \textsc{The Art of the Game}}
\end{center}
\begin{center}
Quiz 1 Solutions
\end{center}
%\date{September 26, 2014}
\renewcommand{\arraystretch}{2}

\vskip .1in
\noindent 1: The objective of the game is to get as points as \underline{\hspace{1cm}} points as possible.
\vskip 0.1 in
\indent \textbf{Answer: few} 

\vskip 0.16in

\vskip .1in
\noindent 2: What suit is each worth 1 point?
\vskip 0.1 in
\indent \textbf{Each HEART is worth 1 point.}

\vskip 0.16in

\vskip .1in
\noindent 3: What card is worth 13 points? (Put your answer in the form of Value, Suit) 
\vskip 0.1 in
\indent \textbf{Queen, Spades}

\vskip 0.16in

\vskip .1in
\noindent 4: The first player to act for a particular trick (hand) plays an 8 diamonds. Now it is Bianca's turn. Bianca has only one diamond, the Ace diamond. She's worried others after her will place down point cards, and she will win the hand. She thinks about placing down another card instead. Should she do this?
\vskip 0.1 in
\indent \textbf{No, it is cheating.}

\vskip 0.16in

\vskip .1in
\noindent 5: For the question above,  imagine that Bianca had no diamonds. Is she allowed to play a suit other than diamonds
\vskip 0.1 in
\indent \textbf{Biancia has to play a card and since she no longer has any diamonds, she now must play a suit other than diamonds.}

\vskip 0.16in

\vskip .1in
\noindent 6: Which player would collect this trick (hand)? (Player A: 8 Spades, Player B: 10 Spades, Player C: Jack Spades, and Player D: 9 Spades)
\vskip 0.1 in
\indent \textbf{Player A starts with a spades so whoever played the highest Spade in this trick takes the hand. In this case, it would be player C.}

\vskip 0.16in

\noindent 7: Which player would collect this trick (hand)? (Player A: 6 Diamonds, Player B: King Hearts, Player C: 10 Diamonds, and Player D: Queen Spades)
\vskip 0.1 in
\indent \textbf{Player A starts with Diamonds so whoever played the highest Diamond in this trick takes the hand. In this case, it would be player C again.}

\vskip 0.16in

\noindent 8: Is it a good idea to pass all of your spades? (assuming you don't have all high-card spades)
\vskip 0.1 in
\indent \textbf{Often times, beginners will try this to get rid of a suit so that whenever a suit is played, they can play whatever they want on top of it. However, with Spades, in the passing phase, if you get passed a Queen, King, or Ace, you are now in huge trouble.}

\vskip 0.16in

\noindent 9: Cooperation is allowed in Hearts. Can you show other people what cards you have?
\vskip 0.1 in
\indent \textbf{You are allowed to tell others what cards you have, but you can not directly SHOW them what card you have. (You can lie about what cards you have.)}

\vskip 0.16in

\noindent 10: Which player would collect this trick (hand)? (Player A: 2 Clubs, Player B: Ace Clubs, Player C: Jack Clubs, and Player D: 4 Hearts)
\vskip 0.1 in
\indent \textbf{This was a tricky question. Since the 2 of Clubs is played, it is the first turn. However, we see that Player D has broken hearts. Therefore this hand is illegal.}

\end{document}