\documentclass[11.5pt]{article}

%\usepackage{geometry}
\usepackage[inner=0.9in,outer=0.9in,top=2.5cm,bottom=2.5cm]{geometry}
\pagestyle{empty}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{fancyhdr, lastpage, bbding, pmboxdraw}
\usepackage[usenames,dvipsnames]{color}
\definecolor{darkblue}{rgb}{0,0,.6}
\usepackage[colorlinks,pagebackref,pdfusetitle,urlcolor=darkblue,citecolor=darkblue,linkcolor=darkred,bookmarksnumbered,plainpages=false]{hyperref}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\pagestyle{fancyplain}
\fancyhf{}
\lhead{ \fancyplain{}{The Art of the Game} }
%\chead{ \fancyplain{}{} }
\rhead{ \fancyplain{}{\today} }

\thispagestyle{plain}

%%%%%%%%%%%% LISTING %%%
\usepackage{listings}
\usepackage{caption}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\textwidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}
\usepackage{verbatim} % used to display code
\usepackage{fancyvrb}
\usepackage{acronym}
\usepackage{amsthm}
\VerbatimFootnotes % Required, otherwise verbatim does not work in footnotes!
\usepackage[utf8]{inputenc}
\usepackage{enumitem}




\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{CadetBlue}{cmyk}{0.62,0.57,0.23,0}
\definecolor{lightlightgray}{gray}{0.93}



\lstset{
%language=bash,                          % Code langugage
basicstyle=\ttfamily,                   % Code font, Examples: \footnotesize, \ttfamily
keywordstyle=\color{OliveGreen},        % Keywords font ('*' = uppercase)
commentstyle=\color{gray},              % Comments font
numbers=left,                           % Line nums position
numberstyle=\tiny,                      % Line-numbers fonts
stepnumber=1,                           % Step between two line-numbers
numbersep=5pt,                          % How far are line-numbers from code
backgroundcolor=\color{lightlightgray}, % Choose background color
frame=none,                             % A frame around the code
tabsize=2,                              % Default tab size
captionpos=t,                           % Caption-position = bottom
breaklines=true,                        % Automatic line breaking?
breakatwhitespace=false,                % Automatic breaks only at whitespace?
showspaces=false,                       % Dont make spaces visible
showtabs=false,                         % Dont make tabls visible
columns=flexible,                       % Column format
morekeywords={__global__, __device__},  % CUDA specific keywords
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{center}
{\Large \textsc{The Art of the Game}}
\end{center}
\begin{center}
Quiz 1 Solutions
\end{center}
%\date{September 26, 2014}
\renewcommand{\arraystretch}{2}

\vskip .1in
\noindent 1: Are you allowed to play a development card the turn you buy it?
\vskip 0.1 in
\indent \textbf{Answer: Yes, but only if the development card is a Victory Point and it brings me to 10 points.} 

\vskip 0.16in

\vskip .1in
\noindent 2: Are you allowed to play a development card before you roll the die??
\vskip 0.1 in
\indent \textbf{No}

\vskip 0.16in

\vskip .1in
\noindent 3: What does rolling a 7 allow you to do (mark all that apply)?
\vskip 0.1 in
\indent \textbf{There is no space on the board with a 7 on it. When a 7 is rolled, everyone who has strictly more than 7 (8 or more) cards must discard half of their cards rounding down. In addition to this, the player that rolled a 7, must move the robber to a new location and he or she is also allowed to steal a resource from any player who owns a settlement adjacent to the tile the robber was moved to. }

\vskip 0.16in

\vskip .1in
\noindent 4: What do you need to build a settlement (mark all that apply)?
\vskip 0.1 in
\indent \textbf{Wood, Brick, Wheat, Sheep}

\vskip 0.16in

\vskip .1in
\noindent 5: For the following image, where is an acceptable location for the red player to build a settlement?
\vskip 0.1 in
\indent \textbf{The rules of Catan say that a player is not allowed to build a settlement on a spot adjacent to another settlement.}

\vskip 0.16in

\vskip .1in
\noindent 6: Which player would collect this trick (hand)? (Player A: 8 Spades, Player B: 10 Spades, Player C: Jack Spades, and Player D: 9 Spades)
\vskip 0.1 in
\indent \textbf{Player A starts with a spades so whoever played the highest Spade in this trick takes the hand. In this case, it would be player C.}

\vskip 0.16in

\noindent 7: Which player would collect this trick (hand)? (Player A: 6 Diamonds, Player B: King Hearts, Player C: 10 Diamonds, and Player D: Queen Spades)
\vskip 0.1 in
\indent \textbf{Player A starts with Diamonds so whoever played the highest Diamond in this trick takes the hand. In this case, it would be player C again.}

\vskip 0.16in

\noindent 8: Is it a good idea to pass all of your spades? (assuming you don't have all high-card spades)
\vskip 0.1 in
\indent \textbf{Often times, beginners will try this to get rid of a suit so that whenever a suit is played, they can play whatever they want on top of it. However, with Spades, in the passing phase, if you get passed a Queen, King, or Ace, you are now in huge trouble.}

\vskip 0.16in

\noindent 9: Cooperation is allowed in Hearts. Can you show other people what cards you have?
\vskip 0.1 in
\indent \textbf{You are allowed to tell others what cards you have, but you can not directly SHOW them what card you have. (You can lie about what cards you have.)}

\vskip 0.16in

\noindent 10: Which player would collect this trick (hand)? (Player A: 2 Clubs, Player B: Ace Clubs, Player C: Jack Clubs, and Player D: 4 Hearts)
\vskip 0.1 in
\indent \textbf{This was a tricky question. Since the 2 of Clubs is played, it is the first turn. However, we see that Player D has broken hearts. Therefore this hand is illegal.}

\end{document}